---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r, echo = TRUE}
unzip("activity.zip")
activity <- read.csv("activity.csv", header=TRUE, sep=",")
activity$steps <- ifelse(is.na(activity$steps), 0, activity$steps) #replace NA with 0 in "steps" column
summary(activity)
```


## What is mean total number of steps taken per day?\  
1. Make a histogram of the total number of steps taken each day
```{r, echo=TRUE}
steps.perdate <- aggregate(steps ~ date, data=activity, FUN=sum)
hist(steps.perdate$steps, xlab="Steps per day", ylim=c(0,30),
     main="Histogram of total steps per day")
```
  
2. Calculate and report the mean and median of the total number of steps taken per day
```{r, echo=TRUE}
mean(steps.perdate$steps)
median(steps.perdate$steps)
```


## What is the average daily activity pattern?  
1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r, echo=TRUE}
steps.interval <- aggregate(steps ~ interval, data = activity, FUN=mean)
plot(steps ~ interval, data=steps.interval, type="l", 
     xlab="Interval in 5 mins", ylab="Average steps")
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
